CHEC Study Sweat Chloride

### 2025-02-05 Edith Zemanick/Sweat Variability/sweat_test_analysis_chec.qmd
model ideas CHEC

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(readxl)
library(arsenal)
library(ggpubr)
library(performance)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Variability")
```

@@

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(tidyverse)
library(readxl)
library(arsenal)
library(ggpubr)
library(lmerTest)
library(performance)
knitr::opts_knit$set(root.dir = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Variability")
```

@@

# Model-based approaches

```{r}
m <- glmer(pre_post ~ na + cl + (1 | subject), data = chec_long, family = "binomial")
m2 <- lmer(cl ~ pre_post * na + (1 | subject), data = chec_long)
```
